Biogeography and Environmental Conditions Shape Phage and Bacteria Interaction Networks Across the Healthy Human Microbiome

### 2017-02-15 doc/manuscript.Rmd
Updated word counts.
Updated the smaller format things.
Made font and organization updates.

---
title: Biogeography and Environmental Conditions Shape Phage and Bacteria Interaction Networks Across the Healthy Human Microbiome
author: 
- name: Geoffrey D Hannigan
  affiliation: 1
- name: Melissa B Duhaime
  affiliation: 2
- name: Danai Koutra
  affiliation: 3
- name: Patrick D Schloss
  affiliation: 1,\*
address:
  - code: 1
    address: Department of Microbiology & Immunology, University of Michigan, Ann Arbor, Michigan, 48108
  - code: 2
    address: Department of Ecology and Evolutionary Biology, University of Michigan, Ann Arbor, Michigan, 48108
  - code: 3
    address: Department of Computer Science, University of Michigan, Ann Arbor, Michigan, 48108
  - code: \*
    address: To whom correspondence may be addressed.
output:
  md_document:
    variant: markdown
---

@@

@@

***Text Length***: 34,039 / 50,000 Characters

\* *Figures included for internal editing purposes*

@@

>>>>

---
title: Biogeography and Environmental Conditions Shape Phage and Bacteria Interaction Networks Across the Healthy Human Microbiome
author: 
- name: Geoffrey D Hannigan
  affiliation: 1
- name: Melissa B Duhaime
  affiliation: 2
- name: Danai Koutra
  affiliation: 3
- name: Patrick D Schloss
  affiliation: 1,\*
address:
  - code: 1
    address: Department of Microbiology & Immunology, University of Michigan, Ann Arbor, Michigan, 48108
  - code: 2
    address: Department of Ecology and Evolutionary Biology, University of Michigan, Ann Arbor, Michigan, 48108
  - code: 3
    address: Department of Computer Science, University of Michigan, Ann Arbor, Michigan, 48108
  - code: \*
    address: To whom correspondence may be addressed.
output:
  md_document:
    variant: markdown
fontsize: 11pt
mainfont: 'Helvetica'
---

@@

***Running Title***: Network Diversity of the Healthy Human Microbiome

@@

***Text Length***: 35,640 / 50,000 Characters

\* *Figures at the end of the document for internal review only.*

@@

# Disclosure Declaration
The authors report no conflicts of interest.
